Optical Music Recognition for Homophonic LilyPond File Generation

### 2024-05-10 papers/cs444/paper-cs444.tex
cover page
more progress! MOREgit add -A!

\title[omr-lilypond-midi]{Optical Music Recognition for Homophonic LilyPond File Generation}
\author{Evan Matthews}
\email{evanmm3@illinois.edu}
%\orcid{1234-5678-9012}
\affiliation{%
	\institution{University of Illinois Urbana-Champaign}
	\country{}
}

\begin{abstract}
\todo{Abstract}
\end{abstract}

@@

@@

\subsection{CRNN Model}
\todo{CRNN model}
The proposed Image-to-MIDI model is a toy implementation of Shi, et al.'s pioneering work in CRNNs~\cite{shi2015endtoend}.

@@

\section{Results}

\section{Discussion}
\todo{discussion}

>>>>

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}

        \Huge
        \textbf{Optical Music Recognition for Homophonic LilyPond File Generation}

        \vspace{0.5cm}
        \LARGE

        \vspace{0.5cm}

        \textbf{Evan Matthews}

        \vspace{0.9cm}
		\textbf{Executive Summary}

		\vspace{0.5cm}
		abstract goes here...

		\begin{figure}
			\centering
			\includegraphics[width = .8\linewidth]{./figures/cover.png}
		\end{figure}

        \vfill

        \vspace{0.8cm}

        \Large
        Department of Computer Science\\
        University of Illinois Urbana-Champaign\\
        United States\\
        May 10th, 2024

    \end{center}
\end{titlepage}

\title[omr-lilypond-midi]{Optical Music Recognition for Homophonic LilyPond File Generation}
\author{Evan Matthews}
% \email{evanmm3@illinois.edu}
% %\orcid{1234-5678-9012}
% \affiliation{%
% 	\institution{University of Illinois Urbana-Champaign}
% 	\country{}
% }

% \begin{abstract}
% \todo{Abstract}
% \end{abstract}

@@

For \textbf{RQ1}, I aim to recover noticeable results regarding the CRNN model's ability to generalize sequences of data from scores.
Hence, whether or not order-dependent training can pick up on note, rhythm or duration sequences will be crucial to my final analysis.
Next, promising results from \textbf{RQ1} will be compared against existing research to answer \textbf{RQ2}. 
In particular, the generalized CRNN model's ability to render score data as Lilypond (.ly) files is compared against other notation systems to determine if a more complex Lilypond-based model would be successful.
Finally, for \textbf{RQ3}, the results of CRNN model training are criticized on what should be generalized or further implemented in order to reliably translate score images into Lilypond data.
This research question refers to all-encompassing limitations such as in \textbf{1.2} along with experiment-specific limitations.

@@

\subsection{CRNN Model}
\todo{CRNN model}
The proposed Image-to-MIDI model is a smaller model referencing Shi, et al.'s pioneering work in the creation of CRNNs~\cite{shi2015endtoend}.
The model itself consists of multiple two-dimensional Convolutional/MaxPooling pairs for the purpose of extracting features from the intial score images.
Batch normalization layers are also applied to refine data recovered from the feature extraction.
Lastly, features are pushed through two bidirectional LSTM layers- the recurrent layers of the model- for data prediction with respect to "sequences" of the images.
In this case, sequences of the image data are the pixel columns of $(595 \times H)$ images, where $H$ is the height of the image dependent on the overall "length" of the music.

\begin{figure}
	\centering
	\includegraphics[width = .8\linewidth]{./figures/crnn_arch.png}
	\caption{General CRNN architecture, as modeled by Shi, et al. ~\cite{shi2015endtoend}}
	\label{fig:crnn-arch}
\end{figure}

@@

\section{Results}
\todo{results}

\section{Discussion}

The following section details my analysis with respect to previously discussed research questions.

\subsection{Model Generalization (RQ1)}

\subsection{Format Comparison (RQ2)}

\subsection{Model Criticism (RQ3)}
